%
\newpage

\subsection{add\_on\_axis\_fields}

\begin{itemize}

\item {\bf description:}

Adds on-axis field data to the simulation.  The user must provide an
SDDS file giving $E_z(z,r=0)$.  This data is used to compute
$E_z(z,r,t)$, $E_r(z,r,t)$, and $B_\phi(z,r,t)$ using an off-axis
expansion in $r$ and assuming $E \sim \sin
(\omega t + \phi)$ and $B \sim \cos (\omega t + \phi)$.

Any number of \verb|add_on_axis_fields| commands may be given.

\item {\bf example:} 
\begin{verbatim}
&add_on_axis_fields
  filename = fieldProfile.sdds,
  z_name = z,
  Ez_name = Ez,
  Ez_peak = 30e6,
  phase = 180,
  expansion_order = 2
  fields_used = fieldUsed.sdds,
&end
\end{verbatim}

This command loads on-axis field data from columns \verb|z| and
\verb|Ez| in \verb|fieldProfile.sdds|, and scales it so that the peak
field is 30 MV/m.  The phase, $\phi$, is set to 180 degrees.  Because
\verb|spiffe| simulates electrons, if $E(z,r)$ is positive, the phase
factor must be negative to provide acceleration.  I.e.,
$\phi=270^\circ$ is the accelerating phase.

\item {\bf synopsis and defaults:} 
\begin{verbatim}
#namelist add_on_axis_fields
        STRING filename = NULL;
        STRING z_name = NULL;
        STRING Ez_name = NULL;
        double Ez_peak = 0;
        double frequency = 0;
        double z_offset = 0;
        long expansion_order = 3;
        STRING fields_used = NULL;
#end
\end{verbatim}

\item {\bf details:} 
\begin{itemize}
\item {\tt filename}: Name of the SDDS file containing the data.
\item {\tt z\_name}: Name of the column containing $z$ values, which must be monotonically increasing and
  equispaced.
\item {\tt Ez\_name}: Name of the column containing $E_z$ values.
\item {\tt Ez\_peak}: Absolute value, in V/m, of the maximum on-axis electric field due to this field profile.
  The $E_z$ values are scaled to obtain this maximum, but the signs are unchanged.
\item {\tt frequency}: Frequency of the fields, in Hz.
\item {\tt z\_offset}: Offset, in meters, to be added to the $z$ values.
\item {\tt expansion\_order}: Order of the off-axis expansion:
  \begin{itemize}
   \item[0] $E_z$ is constant in $r$, while $E_r$ and $B_\phi$ are zero.
   \item[1] $E_z$ is constant in $r$, while $E_r$ and $B_\phi$ vary linearly with $r$.
   \item[2] Adds a quadratic variation with $r$ to $E_z$ .
   \item[3] Adds a cubic variation with $r$ to $E_r$ and $B_\phi$.
  \end{itemize}
\item {\tt fields\_used}: Name of an SDDS file to which field profile data will be written for all
  on-axis fields specified up to and including this command.
\end{itemize}

\end{itemize}
