%
\newpage

\subsection{define\_antenna}

\begin{itemize}

\item {\bf description:}
Allows generating time-varying fields using a modulated sine-wave current
source.

\item {\bf example:} 
\begin{verbatim}
&define_antenna
    start = 0.01, end = 0.02, position = 0.03,
    direction = "z",
    current = 1,
    frequency = 2856e6,
    waveform = "spline.wf"
&end
\end{verbatim}
This defines a current source in the longitudinal direction extending from
z of 1cm to 2cm at a radius of 3cm.  The amplitude of the current is
1A with a frequency of 2856MHz, modulated by the envelope in SDDS file
{\tt spline.wf}.

\item {\bf synopsis and defaults:} 
\begin{verbatim}
&define_antenna
    double start = 0;
    double end = 0;
    double position = 0;
    STRING direction = "z";
    double current = 0;
    double frequency = 0;
    double phase = 0;
    STRING waveform = NULL;
    double time_offset = 0;
&end
\end{verbatim}

\item {\bf details:} 

\begin{itemize}
\item {\tt direction}: may take values "z" and "r", indicating an antenna extending
        in the longitudinal or radial direction, respectively.
\item {\tt start, end}:  starting and ending limits of the antenna in the 
        {\tt direction} direction.
\item {\tt position}: position of the antenna in the "other" direction.  I.e., it is
        the r position if {\tt direction} is "z", and the z position if {\tt direction}
        is "r".
\item {\tt current, frequency, phase}: basic parameters of the antenna waveform.
\item {\tt waveform, time\_offset}: specifies an envelope function for the antenna drive.
The SDDS file {\tt waveform} must contain at least two columns, named {\tt t} (for the
time in seconds) and {\tt W}, specifying the envelope {\tt W(t)}.  The antenna is
driven by the function
$ I*W(t-t_o)*\sin(2*\pi*f+\phi) $, where $I$ is the {\tt current} in Amperes, 
$t$ is the time in seconds, $t_o$ is {\tt time\_offset} in seconds, $f$ is
{\tt frequency} in Hertz, and $\phi$ is {\tt phase} in radians.

\end{itemize}

\end{itemize}
