%
\newpage

\subsection{load\_particles}

\begin{itemize}

\item {\bf description:}

Allows loading particles from an SDDS file.  This is an alternative to using
a cathode and can provide essentially arbitrary particle distributions.
Since \verb|spiffe| is a 2.5 dimensional code, the ``particles'' are really
rings at a given radius and longitudinal position.

Note that particles can be injected into the simulation region if they start with
$z$ or $r$ coordinates outside of $z:[z_{\textrm{min}}, z_{\textrm{max}}]$ 
or $r:[0, r_{\textrm{max}}]$. In this case, the particles drift ballistically until
they enter the problem region. As a special case, particles entering from the 
left-hand side of the problem region are not active until they emerge from
any metal surface that abuts $z=z_{\textrm{min}}$.

\item {\bf example:} 
\begin{verbatim}
&load_particles
    filename = "particles.sdds",
&end
\end{verbatim}
This loads particles from the file \verb|particles.sdds|.

\item {\bf synopsis and defaults:} 
\begin{verbatim}
#namelist load_particles
        STRING filename = NULL;
        long sample_interval = 1;
        double stiffness = 1;
#end
\end{verbatim}

\item {\bf details:}
\begin{itemize}
\item {\tt filename}: Name of the SDDS file from which to take particle data.
  The file must have the following columns with the following units:
  \begin{itemize}
    \item[z]: longitudinal position in meters. 
    \item[r]: radial poition in meters.  If the particle position is initially
       outside the problem region or inside a metal volume, it will move 
       ballistically until it enters the problem region or emerges from the metal.
    \item[pz]: longitudinal momentum, $\beta_z \gamma$.
    \item[pr]: radial momentum, $\beta_r \gamma$.
    \item[pphi]: azimuthal momentum, $\beta_\phi \gamma$.
    \item[q]: charge, in Coulombs.
    \end{itemize}

\item {\tt sample\_interval}: Causes \verb|spiffe| to take only every
  {\tt sample\_interval}$^{th}$ particle from the file.

\item {\tt stiffness}: Allows making the beam artificially stiff.  Equivalent
  to increasing the particle mass by the given factor.

\end{itemize}

\end{itemize}


